\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-28 paper/chaining.tex
Fix graph in Sec. 3
Fix graphs in sec. 4

%Adding additional line breaks to this section will interfere with the formatting.
\begin{figure*}[t]
\centering
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.99\textwidth]{runtime.pdf}
\captionsetup{justification=centering}
\caption{Protocol Runtime}
\label{fig:runtime}
\end{subfigure}\hfill
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.99\textwidth]{cputime.pdf}
\captionsetup{justification=centering}
\caption{CPU Time}
\label{fig:cputime}
\end{subfigure}\hfill
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.99\textwidth]{bandwidth.pdf}
\captionsetup{justification=centering}
\caption{Network Data}
\label{fig:data}
\end{subfigure}
\caption{Performance of Lawful Contact-Chaining}
\label{fig:performance}
\end{figure*}

>>>>

%Adding additional line breaks to this section will interfere with the formatting.
\begin{figure*}[t]
\centering
\begin{subfigure}{0.66\columnwidth}
\centering
\begin{tikzpicture}[scale=0.66]
\begin{loglogaxis}[
	title={Protocol Runtime},
	title style={font=\Large,},
	xlabel={Ciphertexts in Result},
	ylabel={Running Time [min]},
	ylabel style={overlay, anchor=north,},
	xmin=10, xmax=1000000,
	ymin=0.01, ymax=100,
	%xtick={10, 100, 1000, 10000, 100000},
	%ytick={0.01, 0.1, 1, 10, 100, 1000},
	log ticks with fixed point,
	legend pos=north west,
	ymajorgrids=true,
	xmajorgrids=true,
	grid style=dashed,
	legend style={cells={anchor=west}},
]
\addplot[
	color=blue,
	mark=o,
	only marks,
	mark size=1pt,
	]
	table [x=Ciphertexts, y=RunningTime, col sep=comma] {chainingrsa.csv};	
\addplot[
	color=red,
	mark=square,
	only marks,
	mark size=1pt,
	]
	table [x=Ciphertexts, y=RunningTime, col sep=comma] {chainingnocrypto.csv};
\legend{Lawful contact-chaining, Zero-crypto}
\end{loglogaxis}
\end{tikzpicture}
%\captionsetup{justification=centering}
%\caption{Protocol Runtime}
\label{fig:runtime}
\end{subfigure}\hfill
\begin{subfigure}{0.66\columnwidth}
\centering
\begin{tikzpicture}[scale=0.66]
\begin{loglogaxis}[
	title={All-Telecom CPU Time},
	title style={font=\Large,},
	xlabel={Ciphertexts in Result},
	ylabel={Total CPU Time [min]},
	ylabel style={overlay, anchor=north,},
	xmin=10, xmax=1000000,
	ymin=0.1, ymax=1000,
	%xtick={10, 100, 1000, 10000, 100000},
	%ytick={0.01, 0.1, 1, 10, 100, 1000},
	log ticks with fixed point,
	legend pos=north west,
	ymajorgrids=true,
	xmajorgrids=true,
	grid style=dashed,
	legend style={cells={anchor=west}},
]
\addplot[
	color=blue,
	mark=o,
	only marks,
	mark size=1pt,
	]
	table [x=Ciphertexts, y=CPUTime, col sep=comma] {chainingrsa.csv};
\addplot[
	color=red,
	mark=square,
	only marks,
	mark size=1pt,
	]
	table [x=Ciphertexts, y=CPUTime, col sep=comma] {chainingnocrypto.csv};
\legend{Lawful contact-chaining, Zero-crypto}
\end{loglogaxis}
\end{tikzpicture}
%\captionsetup{justification=centering}
%\caption{CPU Time}
\label{fig:cputime}
\end{subfigure}\hfill
\begin{subfigure}{0.66\columnwidth}
\centering
\begin{tikzpicture}[scale=0.66]
\begin{loglogaxis}[
	title={Data transferred},
	title style={font=\Large,},
	xlabel={Ciphertexts in Result},
	ylabel={Data transferred [MB]},
	ylabel style={overlay, anchor=north,},
	xmin=10, xmax=1000000,
	ymin=0.1, ymax=10000,
	%xtick={10, 100, 1000, 10000, 100000},
	%ytick={0.01, 0.1, 1, 10, 100, 1000},
	log ticks with fixed point,
	legend pos=north west,
	ymajorgrids=true,
	xmajorgrids=true,
	grid style=dashed,
	legend style={cells={anchor=west}},
]
\addplot[
	color=blue,
	mark=o,
	only marks,
	mark size=1pt,
	]
	table [x=Ciphertexts, y=Bytes, col sep=comma] {chainingrsa.csv};	
\addplot[
	color=red,
	mark=square,
	only marks,
	mark size=1pt,
	]
	table [x=Ciphertexts, y=Bytes, col sep=comma] {chainingnocrypto.csv};
\legend{Lawful contact-chaining, Zero-crypto}
\end{loglogaxis}
\end{tikzpicture}
%\captionsetup{justification=centering}
%\caption{Network Data}
\label{fig:data}
\end{subfigure}
\captionsetup{justification=centering}
\caption{Performance of Lawful Contact-Chaining}
\label{fig:performance}
\end{figure*}
